---
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Ensure that random variables are repeatable:
set.seed(10)
```

# Descriptive Statistics

This document can be used to quickly analyze and record the statistics for a given population.  The statistics measured in this document include the mean, variance, standard deviation, range, median, quartiles, and interquartile range.

```{r default_variables, include=FALSE}
# countData: count of observations in the simulated data.
countData = 1000

# expectedMean: expected mean of the population.
expectedMean = 0

# standard_deviation: standard deviation of the simulated group of numbers.
standard_deviation = 1

# nDigits: The count of significant digits used when printing the results.
nDigits = 3

# bScientific: Turns on or off scientific notation for results.
bScientific = TRUE
```
```{r r_stats_mean__data, include=FALSE}
# Prepare a set of data to demonstrate this operation.  Use a matrix for later expansion
data = matrix(rnorm(n = countData, mean = expectedMean, sd = standard_deviation), nrow = 1000, ncol = 1)
```
```{r r_stats_descriptive, include=FALSE}
# Calculate the variance of the data
varianceData = var(data)

# Calculate the standard deviation of the data
stdDevData = sd(data)
```

### Results

Modify this document to include an analysis of the following descriptive statistics.  Be sure to consider whether it is appropriate to include a **mode**, etc. analysis on a numeric value or any set of data that is not likely to be appropriately categorized when discussing these results with less-technical audiences.

The following histogram shows the general distribution of the data:

```{r histData}
hist(data)
```

```{r normData}
summary(data)
```
- **Standard Deviation**: `r format(stdDevData, digits = nDigits, scientific = bScientific)`
